Interval Probability for Fuzzy Quantum Theories

### 2016-05-20 prob.tex
prob.tex \section{Quantum Probability Spaces} updates...

\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}
\yutsung{The definition of independence is different from different
sources:
\begin{enumerate}
\item In Swart's~\cite{Swart2013}, two $*$-algebras~$\mathscr{A}_{1}$ and
$\mathscr{A}_{2}$ which commute with each other are \emph{logically
independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu_{1}\otimes\mu_{2}$
on $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$ such that
$\left(\mu_{1}\otimes\mu_{2}\right)\left(A_{1}\otimes
A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.\\
Then, Swart proved the Bell inequality on logically independence $*$-algebras
with product state. It is good that independence is tied up with Bell
inequality, but the problem for us is that this defines the independent of
algebras, but not events\ldots
\item In Yuan's~\cite{Yuan2012}, given a $\mu$ on an $*$-algebra~$\mathscr{A}$,
two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are independent
if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
The same problem as the previous one: this defines the
independent of algebras, but not events\ldots
\item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
we need first understand their notation because they focused on the
hidden-variable (HV) models. Let $\lambda$ is the HV, $A_{i}$ is
the measurement of the observable~$A$ at the position $i$ in the
sequence. For example, $A_{1}B_{2}C_{3}$ denotes the sequence of
measuring $A$ first, then $B$, and finally $C$. We assume the outcome
of an observable is deterministic by $\lambda$. For example, the
outcome of $B_{2}$ from the preceding sequence is denoted by $v\left(B_{2}\middle|A_{1}B_{2}C_{3}\right)$.
Then, the outcome of $A$ is independent of whether $B$ is measured
before or after $A$ is $v\left(A_{1}\right)=v\left(A_{2}\middle|B_{1}A_{2}\right)$.\\
If the outcomes of compatible observables are independent for any
HV~$\lambda$, the HV model is non-contextual.\\
Compare to the previous definitions, this definition is appealing
in a sense that projection operators are special cases of observables,
and the definition of independence is tied up with contextuality.
However, before adopting their definition, we need to reformulate
the definition to the usual quantum model....
\item For the definition we used last time, given a quantum probability
measure~$\mu:\events\rightarrow[0,1]$, two commuting projections
$P_{1}$ and $P_{2}$ are independent if $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
We have two examples:
\end{enumerate}
}

\yutsung{\begin{example}[Independence of product state] Consider
the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$.
Consider the following projections:
\[
\begin{array}{rcl}
P_{1}=\proj{00}+\proj{01},\quad P_{2}=\proj{00}+\proj{10},\quad P_{3}=\proj{10}+\proj{11},\quad P_{4}=\proj{00}\end{array}
\]
and their probabilities: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/2,\quad\mu\left(P_{4}\right)=1/4\textrm{ .}\end{array}
\]
On one hand, $P_{1}$ and $P_{3}$ are complement to each other so
we have
\begin{eqnarray*}
\mu\left(P_{1}\right)+\mu\left(P_{3}\right) & = & \frac{1}{2}+\frac{1}{2}=1\\
\mu\left(P_{1}\right)\mu\left(P_{3}\right) & = & \frac{1}{4}\ne0=\mu\left(\mathbb{0}\right)=\mu\left(P_{1}P_{3}\right)
\end{eqnarray*}
Therefore, $P_{1}$ and $P_{3}$ commute, but not independent. On
the other hand, $P_{1}$ also commutes with $P_{2}$, and
\begin{eqnarray*}
\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{4}\right)=\mu\left(P_{1}P_{2}\right)
\end{eqnarray*}
so that $P_{1}$ and $P_{2}$ are independent.\qed\end{example}

>>>>

\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\qed\end{definition}
\yutsung{The definition of independence is different from different
sources:
\begin{enumerate}
\item In Swart's~\cite{Swart2013}, given a $*$-algebra~$\mathscr{A}$,
two commuting sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{logically
independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu$
on the smallest sub-$*$-algebra of $\mathscr{A}$ containing both
$\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ such that $\mu\left(A_{1}
A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$. If two
sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are logically
independent, the smallest sub-$*$-algebra containing both $\mathscr{A}_{1}$ and
$\mathscr{A}_{2}$ is denoted by $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$, and
its probability measure~$\mu$ is denoted by $\mu_{1}\otimes\mu_{2}$\\
Then, Swart proved the Bell inequality on logically independence $*$-algebras
with a product state which gives a clear physical meaning. However, this
only defines the independence of algebras instead of events.
\item In Yuan's~\cite{Yuan2012}, given a $\mu$ on a $*$-algebra~$\mathscr{A}$,
two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are \emph{independent}
if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
The same problem as the previous one: this defines the
independent of algebras, but not events. Morever, I haven't found a clear
physical meaning of this definition, yet\ldots
\item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
we need to first understand their notation because they focused on the
hidden-variable (HV) models. Let $\lambda$ is the HV, $A_{i}$ is
the measurement of the observable~$A$ at the position $i$ in the
sequence. For example, $A_{1}B_{2}C_{3}$ denotes the sequence of
measuring $A$ first, then $B$, and finally $C$. Given a fixed $\lambda$, we
assume the outcome of an observable is deterministic. For example, the
outcome of $B_{2}$ from the preceding sequence is denoted by $v\left(B_{2}\middle|A_{1}B_{2}C_{3}\right)$.
Then, the outcome of $A$ is \emph{independent} of whether $B$ is measured
before or after $A$ is $v\left(A_{1}\right)=v\left(A_{2}\middle|B_{1}A_{2}\right)$.\\
If the outcomes of compatible observables are independent for any
HV~$\lambda$, the HV model is non-contextual. (Notice that they have their own
definition of ``compatible observables'' for their HV model\ldots)\\
Compare to the previous definitions, this definition is appealing
in a sense that projection operators are special cases of observables,
and this definition has a physical meaning related to contextuality.
However, before adopting their definition, we need to reformulate
the definition to the usual quantum model....
\item For the definition we used last time, given a quantum probability
measure~$\mu:\events\rightarrow[0,1]$, two commuting projections
$P_{1}$ and $P_{2}$ are independent if $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
We have two examples:
\end{enumerate}
}

\yutsung{\begin{example}[Independence of product state] Consider
the 2-qubit Hilbert space with a probability measure~$\mu\left(P\right)=\melement{\ps\ps}{P}$
with the following projections:
\[
\begin{array}{rcl}
P_{1}=\proj{00}+\proj{01},\quad P_{2}=\proj{00}+\proj{10},\quad P_{3}=\proj{10}+\proj{11},\quad P_{4}=\proj{00}\end{array}
\]
and their probabilities: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(P_{1}\right)=1/2,\quad\mu\left(P_{2}\right)=1/2,\quad\mu\left(P_{3}\right)=1/2,\quad\mu\left(P_{4}\right)=1/4\textrm{ .}\end{array}
\]
On one hand, $P_{1}$ and $P_{3}$ are complement to each other so
we have
\begin{eqnarray*}
\mu\left(P_{1}\right)+\mu\left(P_{3}\right) & = & \frac{1}{2}+\frac{1}{2}=1\\
\mu\left(P_{1}\right)\mu\left(P_{3}\right) & = & \frac{1}{4}\ne0=\mu\left(\mathbb{0}\right)=\mu\left(P_{1}P_{3}\right)
\end{eqnarray*}
Therefore, $P_{1}$ and $P_{3}$ commute, but not independent. On
the other hand, $P_{1}$ also commutes with $P_{2}$, and
\begin{eqnarray*}
\mu\left(P_{1}\right)\mu\left(P_{2}\right) & = & \frac{1}{4}=\mu\left(P_{4}\right)=\mu\left(P_{1}P_{2}\right)
\end{eqnarray*}
so that $P_{1}$ and $P_{2}$ are independent.\qed\end{example}
